\section{Introduction}
\label{sec:introduction}

The project is a part of the course ``Software Architecture (TDT4240)'' at
NTNU\@. The goal is to create a multiplayer game running on a mobile device. We were free to choose between Android, iOS and XNA as target platform for our game. The project should cover all aspects of software development from documentation to implementation and testing.

This document describes the implementation of our Android game
``Bedpres-Bingo'', through five chapters.

The chapter ``Design Details'' gives a description of the architecture and highlights interesting classes and how we made measures to ensure modifiability and availability.

The chapter ``User Manual'' gives a description of how to install the game to an Android device and how to play the game.

The chapter ``Test Report'' reports the different tests done and the results of these tests. 

The chapter ``Relationship with architecture'' gives a comparison of the planned architecture and the architecture of the final game. The chapter will also explain why changes were made.

The chapter ``Problems, Issues and Lessons Learned'' will give a description of different problems and issues that occured and how we solved them. The chapter closes with an evaluation and summary of what we learned. 

It is expected that the reader possesses an understanding of softwarearchitecture. To fully understand and enjoy this game, the player should possess a knowledge about what a ``bedpres'' is, and the game should be played during one of these presentations. The conditions for winning are to cross off all the words on the board, where these words typically are buzzwords used by the companies that come to present themselves as a tool to get people to pay attention.
