\section{Problems, Issues and Lessons Learned}
\label{sec:issues}

\subsection{Problems and issues}
The group encountered some issues regarding meeting hours. As each group
of the members has very busy scheduals, it was not easy to find a time
where the group could have regular meetings where every member
had the opportunity to meet.

Another issue the group encountered
was in using the \texttt{Sheep.jar} package. \texttt{Sheep.jar} is not
suitable for a game like ``Bedpres-Bingo'', as it doesn't require game-loops in the same way \texttt{Sheep.jar} provides.

In the end-phase of the implementation, an inertia was discovered in
fetching games from the server. This delay was between 3 and 10 seconds,
and was not desired for a game like ``Bedpres-Bingo'', as users may
experience the need for quick reconnection to the ongoing game. This
was solved by removing the resolving of foreign keys, and resolving
the words like a \texttt{String} separated with commas.

\subsection{Lessons Learned}
From this project, the group have learned that risk analysis are more
significant to execution of the workload than previously concidered.
The absence of cooperation opportunities due to the group members' scheduals,
made it almost impossible to reach the goal of a fully functioning application
at due date.

The choice of solution for the server would most probably not be a good
one for future release, but suffices as a testing environment. An idea
could be to have a complete server package with possibilities for adding
words which the hosts can set up prior to the bedpres.