\section{Introduction}
\label{sec:introduction}
%Finished
The project is a part of the course ``Software Architecture (TDT4240)'' at NTNU. The goal is to create a multiplayer game running on a mobile device. We were free to choose between Android, iOS and XNA as target platform for our game. 
The project should cover all aspects of software development from documentation to implementation and testing. 

This document contains an architectural description of the planned implementation of our system.

The chapter ``Architectural Drivers'' contains a description of the most important aspects that will affect our architecture.

The chapter ``Stakeholders'' contains a description of the different stakeholders and their interest in the project. 

The chapter ``Architectural viewpoint selection'' contains a description of the architecture by means of the 4+1 View Model. 

The chapter ``Architectural tactics'' contains a description of what choices we have made in oder to ensure Modifiability, Testability, Availability, Performance and Usability. 

The chapter ``Architectural patterns'' contains a description of the patterns we have chosen and how they were used in the project.

The chapter ``Views'' contains a visual presentation of the views of the 4+1 View Model. A short description of how the views relate to each other is also given.

The chapter ``Architectural rationale'' gives a rationale for the architectural choices made.

The chapter ``Issues'' gives a short description of what issues and problems occured and how we solved them.

It is expected that the reader possesses an understanding of software
architecture. To fully understand and enjoy this game, the player should
possess a knowledge about what a ``bedpres'' is, and the game should be played
during one of these presentations.
