\section{Functional Requirements} 
\label{sec:functional requirements}

\subsection{Game Concept}
The game is an augmented version of the popular board/gambling game Bingo,
with localized variations and rules. For those familiar with Bingo,
the game should be easy to start playing. Instead of numbers, this augmented
version will feature words instead. The goal of the game is to cross off
different words on your board. Words are crossed off when they are mentioned
during a company presentation at one of the line societies at NTNU, known in
norwegian as a ``bedriftspresentasjon'' or, colloquially, a ``bedpres''.


\subsection{Functional Requirements}
{\bf Definitions}\\
The functional requirements is prioritized on a scale running from Low via Medium to High, where High is the most prioritized note. 
A requirement is marked with ``High'' priority if it is essential for the game to run at all. Requirements marked as High will be implemented first.
A requirement is marked with a ``Medium'' priority if it is non-essential, but will enhance gameplay to an expected standard. 
A requirement is marked with a ``Low'' priority if is a non-essential nice-to-have feature.

{\bf FR1: Choose board size}\\
The admin should be able to change the board size. The standard board size is
4$\times$4.\\
Priority: Medium

{\bf FR2: Set player names}\\
Before the game is started, the players must be allowed to enter a custom
name.\\
Priority: Medium

{\bf FR3: Connect to server}\\
Before the game starts, the device should connect to the server in order to be
a multiplayer game.\\
Priority: High

{\bf FR4: Receive board from server}\\
The server should send all connected players a list containing a random
subset of the words on the server.\\
Priority: High

{\bf FR5: Place words on playing field}\\
The game should place the words received from the server on the playing
field.\\
Priority: High

{\bf FR6: Cross off words}\\
The player should be able to cross off words by touching the cell containing
the word on the board.\\
Priority: High

{\bf FR7: Undo function}\\
If a player crosses off a word by mistake, they should be able to uncheck it by
touching the cell containing the word again.\\
Priority: Medium

{\bf FR8: Check for Bingo}\\
The game logic should check if the player has crossed off all the words on a
vertical, horizontal or diagonal line.\\
Priority: High

{\bf FR9: Check if player is the first to have Bingo}\\
The game should communicate with the server to check if the player is the first
player to get Bingo, Double-Bingo, Triple-Bingo or MEGA-Bingo. See appendix for
Bingo Rules.\\
Priority: High

{\bf FR10: Notify other players that someone has got a Bingo}\\
Whenever someone is the first player to get Bingo, Double-Bingo, Triple-Bingo
or MEGA-Bingo, the server should notify all the clients of this occurence.\\
Priority: Medium


{\bf FR11: Continuing existing game}\\
The players should be able to continue an existing game at a later time if the
connection was lost or the application was exited during a game.\\
Priority: High

{\bf FR12: Game over}\\
When a player has MEGA-Bingo that player has won, and the game is over. The
game must handle the case when a player disconnects or the game is won.\\
Priority: Medium


{\bf FR13: Golden words}\\
The administrators can elect to add golden words to the master list. These
words can, for instance, be used if the hosts wishes to give out gifts. Anyone
who gets a bingo including the golden word is eligible for better prizes.\\
Priority: Low
