\section{Introduction}
\label{sec:introduction}
%Finished
The project is a part of the course ``Software Architecture (TDT4240)'' at NTNU. The goal is to create a multiplayer game running on a mobile device. We were free to choose between Android, iOS and XNA as target platform for our game. 
The project should cover all aspects of software development from documentation to implementation and testing. 

This document describes the requirements of our Android game ``Bedpres-Bingo''.

The document is parted into five chapters, a change log and appendixes. 
The chapter ``Functional Requirements'' describes the functional requirements for our system in order to be a functional and satisfying game.

The chapter ``Quality Requirements'' describes the chosen quality requirements and choices taken in order to suffice these quality requirements.

The chapter ``COTS - Components and Technical Constraints'' describes the different components in our system and the technical constraints the impose on our implementation.

The chapter ``Issues'' describes the issues that occured and how we solved them.

It is expected that the reader possesses an understanding of software
architecture. To fully understand and enjoy this game, the player should
possess a knowledge about what a ``bedpres'' is, and the game should be played
during one of these presentations. The conditions for winning are to cross off
all the words on the board, where these words typically are buzzwords used by
the companies that come to present themselves as a tool to get people to pay
attention.
