\section{Quality Requirements}

{\bf Primary quality attribute: } Modifiability\\
{\bf Secondary quality attribute: } Availability

\subsection{Modifiability}

\subsubsection*{M1: Choose board size}
By default, the board size will be set to 4$\times$4 tiles. 
A modification will be to make it possible for the game admin to choose the
board size, eg. 3$\times$3 and 5$\times$5.

\begin{tabular}{|m{0.3 \textwidth}|m{0.7 \textwidth}|}
\hline
{\bf Portion of scenario} & {\bf Values} \\ \hline
Source & Developer \\ \hline
Stimulus & Change game board size \\ \hline
Artifact & Change the board sent by the server. Change the logic
checking for bingo \\ \hline
Environment & Design time \\ \hline
Response & Extend functionality of the game \\ \hline
Response measure & 8 hours to implement \\ \hline
\end{tabular}
\newline

\subsubsection*{M2: Golden words}
Adding ``Golden words'' to the gameplay. A random word among the already random
words, will be chosen as a ``Golden word''. This will be placed on the board
like a normal word, but will be written in a golden font color. Getting a bingo
with this word included in the bingo can, for instance, be used to give out
bonus prizes.

\begin{tabular}{|m{0.3 \textwidth}|m{0.7 \textwidth}|}
\hline
{\bf Portion of scenario} & {\bf Values} \\ \hline
Source & Developer \\ \hline
Stimulus & Implement golden words \\ \hline
Artifact & Change the words sent by the server. Change the logic
checking for bingo \\ \hline
Environment & Design time \\ \hline
Response & Extend functionality of the game \\ \hline
Response measure & 10 hours to implement \\ \hline
\end{tabular}

\subsubsection*{M3: Admin player}
A master player will have an admin interface to cross off words in the master
word list. If a player tries to cross off the word before it is crossed off in
the master word list, the player will not be allowed to cross off the word by
the server. This is done to secure against cheating.

\begin{tabular}{|m{0.3 \textwidth}|m{0.7 \textwidth}|}
\hline
{\bf Portion of scenario} & {\bf Values} \\ \hline
Source & Developer \\ \hline
Stimulus & Add admin player to avoid cheating \\ \hline
Artifact & Master interface. Implement logic when crossing off words \\ \hline
Environment & Design time \\ \hline
Response & Extend functionality of the game to avoid cheating \\ \hline
Response measure & 25 hours to implement \\ \hline
\end{tabular}

\subsection{Availability}

\subsubsection*{A1: Session ID}
Make a session ID for each connection. Each user will have a session ID, in
case of disconnection. The server will store the board for each player, linked
to the session ID\@. If a user is disconnected, the game can be retrieved using
the session ID, which should be stored locally on the client device.

\begin{tabular}{|m{0.3 \textwidth}|m{0.7 \textwidth}|}
\hline
{\bf Portion of scenario} & {\bf Values} \\ \hline
Source &  Developer \\ \hline
Stimulus &  Secure against loss of games \\ \hline
Artifact &  Server. Session ID saving on client \\ \hline
Environment & Design time\\ \hline
Response & Secure against disconnection \\ \hline
Response measure & 20 hours to implement \\ \hline
\end{tabular}


\subsubsection*{A2: TCP Connection}
Utilize the TCP transport protocol for all communications between the client
and server. This is to ensure that the connections stay up for the duration
of the game.

\begin{tabular}{|m{0.3 \textwidth}|m{0.7 \textwidth}|}
\hline
{\bf Portion of scenario} & {\bf Values} \\ \hline
Source & Developer \\ \hline
Stimulus & Secure against package loss \\ \hline
Artifact & Connection between client and server \\ \hline
Environment & Design time \\ \hline
Response & Secure against package loss in communication between client and
server \\ \hline
Response measure & 14 hours to implement \\ \hline
\end{tabular}

